---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# shsannualreport

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip) [![Travis-CI Build Status](https://api.travis-ci.org/thomascrines/sdrUpload.svg?branch=master)](https://travis-ci.org/thomascrines/sdrUpload)
<!-- badges: end -->

:construction: :construction: :construction: **Package under construction - watch this space for updates** :construction: :construction: :construction:

Use sdrUpload to upload Excel spreadsheets from a specified directory to a named database, and move the files to an 'archive' folder.

## Installation

Install opendatascot from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("thomascrines/sdrUpload")
```

If the above does not work, you can install from source:

1. Go to the sdrUpload [repository](https://github.com/thomascrines/sdrUpload) on GitHub
1. Click **Clone or download** then **Download ZIP**
1. Save the file locally (e.g. your H drive) and Unzip
1. Install with install.packages()

```{r source-installation, eval = FALSE}
install.packages("your/directory/sdrUpload", repos = NULL,
                 type="source", lib = "your/R/package/library/directory")
```
Examples
---------

Write data from Excel sheets contained in a source directory to SDR database tables, and move files to an archive folder:
`sdr_upload("C://example_source", "C://example_archive", "database_name", "server_name")`

Delete a table from a specified connection:
`sdr_delete_table("table name", "database name", "server name")`
